\documentclass[10pt,a4paper]{article}
\usepackage{amsmath,graphicx,subfigure, hyperref, url}

\title{{Master Thesis\\[0.5em]}
       {\bf \huge Development of a game for hand- and eye coordination in children rehabilitation.\\[0.5em]}
       {\bf Weekly Report 17}}
\author{Anna Maria Walach, S121540}
\setlength{\parindent}{0mm}
\setlength{\parskip}{\medskipamount}

\begin{document}

\maketitle

\section*{What has been done this week}
I prepared the table of content for my thesis:
\begin{itemize}


\item Introduction.
  \begin{itemize}
	\item Problem statement. 
	\item  Motivation.
  	\item  Related work. 
  	\item  Project outline. 
  \end{itemize} 
\item Requirements analysis. 
\begin{itemize}
  \item Cerebral palsy. 
  \item Accessible games. 
  \item Development-related requirements.
\end{itemize}
\item Hardware analysis.
\begin{itemize}
  \item Available hardware.
  \item Prioritizing the requirements (MoSCoW analysis).
  \item Results.
  \end{itemize}
\item Design and implementation.
\begin{itemize}
  \item Initial design.
  \item Iterative testing. 
  \item Implementation details. 
  \end{itemize}
\item Results.
\begin{itemize}
  \item Test results.
  \item Discussion. 
  \end{itemize}
\item Conclusions.
\begin{itemize}
  \item Conclusions.
  \item Future work. (new devices)
  \end{itemize}


\end{itemize}


I wrote down an introduction. I implemented significant changes in the game and added sounds and music. I performed few tests on children age 6-11 with encouraging results. 

\section*{Project status according to the study plan}
There is no delay in the plan.

\section*{Plan for the next weeks}
Finish Requirement analysis chapter. Finish Hardware analysis chapter. Meet with therapist and get game evaluation. 

\bibliographystyle{plainurl}
\bibliography{../thesis/bibliography/Bibliography}


\end{document}

