\documentclass[10pt,a4paper]{article}
\usepackage{amsmath,graphicx,subfigure, hyperref}

\title{{Master Thesis\\[0.5em]}
       {\bf \huge Development of a game for hand- and eye coordination in children rehabilitation.\\[0.5em]}
       {\bf Weekly Report 4}}
\author{Anna Maria Walach, S121540}
\setlength{\parindent}{0mm}
\setlength{\parskip}{\medskipamount}

\begin{document}

\maketitle

\section*{What has been done this week}
This week was less efficient then previous ones. I continued on literature study and prepared for next phase of the project.

\subsection*{Literature}
\subsubsection*{Kinect Xbox 360 as a therapeutic modality for children with cerebral palsy in a school environment: a preliminary study.}

Luna-Olivia et al. \cite{game_xbox_360} performed the study, where they tested influence of virtual reality games controlled by low cost console on children with cerebral palsy. They used already existing games to test the theory of positive impact of playing virtual reality games on children psychomotor status. The results showed statistically significant improvement after training period, that remain even after stopping this additional exercise. 

\emph{Notes:}
\begin{itemize}
\item \emph{usefulness} - 5/5
\item \emph{own keywords} - statistics, diagnostic, evaluating 
\item this study is strong evidence for usefulness of this project
\item it has a lot of meaningful references to another studies
\item highly promising results
\item good evaluation schemas
\end{itemize}

\subsection*{Project status according to the study plan}
%all nice and well
At this week, I should be done with studying current solution. Unfortunately I was not able to yet summarize it properly, so it needs to be prolonged up to the next week. On the other hand, I collected enough information to smoothly advance to the next part of the project plan, which is device testing. 

\section*{Plan for the next weeks}
%meetings, meetings, meetings
For the next week, summary of "current solution" should be done in a form of raw version of thesis chapter. I should prepare and send questions to the occupational therapist. I will also prepare protocol for devices testing and start testing them. 
\bibliographystyle{plain} 
\bibliography{../thesis/bibliography/Bibliography}

\end{document}
